---
title: "Comparing Optimization Algorithm Choices in ADMM"
author: "Akarsh Goyal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparing Optimization Algorithm Choices in ADMM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This tutorial shows how to compare perfomance of ADDM solver
for different optimization algorithm choices. In this example,
we will compare Newton-Raphson method and BFGS method.


```{r setup}
library(solvers)
library(lattice)
```

```{r}
# Generating data
n <- 1000
p <- 40
d <- randomProblem(n, p, response = "binomial", density=0.5)
x <- d$x
y <- d$y
```
Now that we have out training data-set, we will use ADMM to 
obtain the fit twice - once with Newton-Raphson as optimization 
algorithm and again with BFGS as optimization algorithm. Note 
that `diagnostics=TRUE` flag is necessary so that solver records 
the metrics at each iteration.

```{r}
# Obtaining the fit for the solvers we want to compare
admm_nr <- ADMM(x, y, family="binomial", opt_algo="nr", alpha=(0.01),diagnostics=TRUE)
admm_bfgs <- ADMM(x, y, family="binomial", opt_algo="bfgs", alpha=(0.01),diagnostics=TRUE)
```
To compare total execution time, we can use `total_time` attribute of the fit.


```{r}
# Comparing total execution time
print(admm_nr$total_time)
print(admm_bfgs$total_time)
```

Now, these fits cannot be directly used to plot as 
they contain a lot of parameter so we'll call a utility 
function that merges the relevant parameter and returns 
a dataframe.

```{r}
# Merging the metrics into one dataframe
f <- mergeFits(admm_nr, admm_bfgs)
```
Finally, now we can generate the loss vs time plot.

```{r, fig.width=10, fig.height=10}
# Plotting objective vs time
plt <- xyplot(loss ~ time, group = solver, data = f, auto.key = list(corner = c(0.9, 0.9)), type = "l")
update(plt, par.settings = list(fontsize = list(text = 18)))
```

