---
title: "Comparing FISTA, ADMM and Proximal Newton"
author: "Akarsh Goyal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparing FISTA, ADMM and Proximal Newton}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This tutorial shows how to compare perfomance of FISTA, ADMM 
and Proximal Newton. We will use 'heart' dataset for the demonstration.


```{r setup}
library(solvers)
library(lattice)
```
Let's load the data..

```{r}
x <- SLOPE::heart$x
y <- SLOPE::heart$y
```

First step is generating fits for each of the algorithms. Note that 
`diagnostics=TRUE` flag is necessary so that solver records 
the metrics at each iteration.

```{r}
# Obtaining the fit for the solvers we want to compare
fista_fit <- FISTA(x, y, family="binomial", alpha=(0.01),diagnostics=TRUE)
admm_fit <- ADMM(x, y, family="binomial", alpha=(0.01),diagnostics=TRUE)
pn_fit <- PN(x, y, family="binomial", alpha=(0.01),diagnostics=TRUE)
```
We haven't specified optimization algorithm choice in ADMM 
so default (L-BFGS) will be used.   

To compare total execution time, we can use `total_time` attribute of the fit.

```{r}
# Comparing total execution time
print(fista_fit$total_time)
print(admm_fit$total_time)
print(pn_fit$total_time)
```

Now, these fits cannot be directly used to plot as 
they contain a lot of parameter so we'll call a utility 
function that merges the relevant parameter and returns 
a dataframe.

```{r}
# Merging the metrics into one dataframe
f <- mergeFits(list(fista_fit, admm_fit, pn_fit))
```
Finally, now we can generate the loss vs time plot.

```{r, fig.width=10, fig.height=10}
# Plotting objective vs time
plt <- xyplot(loss ~ time, group = solver, data = f, auto.key = list(corner = c(0.9, 0.9)), type = "l")
update(plt, par.settings = list(fontsize = list(text = 18)))
```